Notebook of learning from ensemble labels

### 2021-07-14 docs/manuscript_figures.Rmd
Merge some files

>>>>

## Scalars

```{r}
# Single U-Net model with step learning rate
# Get file names
fns <- list.files('results/scalars/single_step_lr', 
                  pattern = 'step_lr',
                  full.names = T)

# Learning rate
step_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Step = Step / 113)

# Scalars
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
unet_step_lr_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113) %>% 
        select(-Wall.time)
})
names(unet_step_lr_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Single U-Net model with compose learning rate
# Get file names
fns <- list.files('results/scalars/single_compose_lr', 
                  pattern = 'compose_lr',
                  full.names = T)

# Learning rate
compose_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Step = Step / 113)

# Scalars
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
unet_compose_lr_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113) %>% 
        select(-Wall.time)
})
names(unet_compose_lr_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Coteaching + single U-Net model
nms <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
fns_cot <- list.files('results/scalars/cot_single/cot', 
                  full.names = T)
stages <- c('8_5_1', '8_5_2', '9_5_1', '9_5_2')

cot_scalars <- lapply(nms, function(nm){
    fns1 <- fns_cot[str_detect(fns_cot, paste0(nm, "1"))]
    fns2 <- fns_cot[str_detect(fns_cot, paste0(nm, "2"))]
    scalar1 <- do.call(rbind, lapply(stages, function(stage){
        fns <- fns1[str_detect(fns1, stage)]
        if (stage == '8_5_2') {
            read.csv(fns) %>%
                mutate(Step = Step/min(Step) + 5)
        } else if (stage == '9_5_1'){
            read.csv(fns) %>%
                mutate(Step = Step/min(Step) + 10)
        } else if (stage == '9_5_2'){
            read.csv(fns) %>%
                mutate(Step = Step/min(Step) + 15)
        } else{
            read.csv(fns) %>%
                mutate(Step = Step/min(Step))
        }
    }))
    scalar2 <- do.call(rbind, lapply(stages, function(stage){
        fns <- fns2[str_detect(fns2, stage)]
        if (stage == '8_5_2') {
            read.csv(fns) %>%
                mutate(Step = Step/min(Step) + 5)
        } else if (stage == '9_5_1'){
            read.csv(fns) %>%
                mutate(Step = Step/min(Step) + 10)
        } else if (stage == '9_5_2'){
            read.csv(fns) %>%
                mutate(Step = Step/min(Step) + 15)
        } else{
            read.csv(fns) %>%
                mutate(Step = Step/min(Step))
        }
    }))
    scalar1 %>% select(-Wall.time) %>% 
        rename(Value_m1 = Value) %>% 
        merge(scalar2 %>% select(-Wall.time) %>% 
                  rename(Value_m2 = Value),
              by = 'Step')
})
names(cot_scalars) <- nms

fns <- list.files('results/scalars/cot_single/single_ctn', 
                  full.names = T)
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
cot_ctn_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113 + 20) %>% 
        select(-Wall.time)
})
names(cot_ctn_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

cot_single_scalars <- lapply(nms, function(nm){
    cot_scalars[[nm]] %>% 
        select(Step, Value_m2) %>% 
        rename(Value = Value_m2) %>% 
        rbind(cot_ctn_scalars[[nm]])
})
names(cot_single_scalars) <- nms

# Plot

aa <- merge(unet_compose_lr_scalars$Water, 
            cot_single_scalars$Water, 
            by = 'Step') %>% 
    rename(Compose = Value.x, Cot = Value.y) %>% 
    pivot_longer(cols = c(Compose, Cot),
                 names_to = 'type', values_to = 'value')
ggplot(aa, aes(x = Step, y = value)) +
    geom_line(aes(color = type, lty = type)) +
    # geom_smooth(aes(color = type)) +
    theme_bw()
```

### 2021-07-14 docs/notebook_learn_dl_ensemble.Rmd
Merge some files

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3' --num_gradual 10
```

```
python hrlcm/fit_compose_lr.py --exp_name unet_single_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

```bash
df -H
cd .local/share/Trash/
rm -rf *
```
##### Check the RAM usage in M

>>>>

Prepare work:

```
scp -r /Volumes/wildebeest/dl_train ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp -r /Volumes/wildebeest/dl_valid ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp -r /Users/pinot/Dropbox/research/hrlcm/results/north/norm_stats ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_valid.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
```

Run models:

```
python hrlcm/fit_compose_lr.py --exp_name unet_single_gl --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
```

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_gl_blind --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
```

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_8 --highest_score 8 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

```bash
df -H
cd ~/.local/share/Trash/
rm -rf *
```
##### Check the RAM usage in M
